ShrinkNets: Learning Network Size while Training

### 2018-02-09 paper/ICML/related_work.tex

\noindent\textbf{Auto-ML: } Some work that focuses on automatically learning
model architecture through the use of genetic algorithms and reinforcement
learning techniques~\cite{DBLP:journals/corr/ZophL16, zoph2017learning}. These
techniques are focused on learning higher-level architectures (e.g.,
building blocks for neural network architectures). In particular, they do not
focus on finding small but well-performing networks for inference, which is the
goal of ShrinkNets.

>>>>

%\noindent\textbf{Auto-ML: } Some work focuses on automatically learning
%model architecture through the use of genetic algorithms and reinforcement
%learning techniques~\cite{DBLP:journals/corr/ZophL16, zoph2017learning}. These
%techniques are focused on learning higher-level architectures (e.g., building
%blocks for neural network architectures). In particular, they require to train
%full models and may take weeks to converge.

%do not
%focus on finding small but well-performing networks for inference, which is the
%goal of ShrinkNets.
%\tim{Argument is not really convincing, but those techniques require to train
%full models and might take weeks to converge. }
